\bf The usage of bootstrap method in shape-restricted regression

### 2023-07-30 Manuscript/Intro.tex
Update Intro.tex

The rest of the paper is organized as the follows. Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals. Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points. Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
explores the case where a combination of the first two scenarios occurs. An  
adjusted bootstrap procedure is proposed as a working solution in this case.  
Section~\ref{Conclusion} concludes with a discussion.

>>>>

The rest of the paper is organized as the follows. Section 
~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of 
bootstrap method for constructing confidence intervals. 
Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example
and the usage of bootstrap to build the pointwise confidence intervals for certain time
points. Section~\ref{Simulation Study} shows a simulation study to assess the 
performance of the methods.
